When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-10-31 doc/paper/vpd_et_paper_hess.tex
the tex file might be important, gotta be a bettter way to test reproducibility that this

% this is used for arkiv submissions
\documentclass[12pt]{article}
\input{def.tex}

@@

\title{When does vapor pressure deficit drive or reduce
  evapotranspiration?}

\author[1]{Adam Massmann\thanks{Corresponding author: akm2203@columbia.edu}}
\author[1]{Pierre Gentine}
\author[1,2]{Changjie Lin}

@@

\maketitle
\begin{abstract}
  \input{abstract}
\end{abstract}

\onehalfspacing

\section{Introduction}

\input{intro.tex}

@@

\section{Conclusions}

\input{conclusions.tex}

\acknowledgments This work used eddy covariance data acquired and shared
by the FLUXNET community, including these networks: AmeriFlux, AfriFlux,
AsiaFlux, CarboAfrica, CarboEuropeIP, CarboItaly, CarboMont,
ChinaFlux, Fluxnet-Canada, GreenGrass, ICOS, KoFlux, LBA, NECC,
OzFlux-TERN, TCOS-Siberia, and USCCC. The ERA-Interim reanalysis data
are provided by ECMWF and processed by LSCE. The FLUXNET eddy covariance
data processing and harmonization was carried out by the European Fluxes
Database Cluster, AmeriFlux Management Project, and Fluxdata project of
FLUXNET, with the support of CDIAC and ICOS Ecosystem Thematic Center,
and the OzFlux, ChinaFlux and AsiaFlux offices. We would like to thank
Dr. Trevor Keenan for providing tools for citation of the FLUXNET2015
dataset, available at
\url{https://github.com/trevorkeenan/FLUXNET_citations}. This material is
based upon work supported by the National Science Foundation Graduate
Research Fellowship under Grant No. DGE 16-44869. All code and data used
in this analysis, including those used to generate the figures and
tables, are publicly available at \url{https://github.com/massma/climate\_et}

\begin{appendices}
  \section{FLUXNET2015 sites}\label{flux_sites}
  % below taken adapted from Trevor Keenan's FLUXNET citations
  % at github.com/trevorkeenan/FLUXNET_citations
  Table A1: Metadata and citations for flux sites used in this analysis. All data are gathered from \url{www.fluxdata.org}, and citations are aggregated using tools available at \url{https://github.com/trevorkeenan/FLUXNET_citations}.
  \begin{longtable}{l l l l l l l}
    \hline
    \textbf{Site} &
    \textbf{PFT} &
    \textbf{Lat} &
    \textbf{Lon} &
    \textbf{Clim\textsuperscript{1}} &
    \textbf{Period} &
    \textbf{References} \\
    [0.5ex]
    \hline
    \input{flux_sites.tex}
    [1ex]
    \hline
  \end{longtable}
  \textsuperscript{1}  K{\"o}ppen Climate classification.
\end{appendices}

\bibliography{references.bib}

>>>>

\documentclass[hess, manuscript]{copernicus}

\usepackage{makecell} \usepackage{multirow} %AM for tables
\usepackage{hyperref}
\usepackage[title]{appendix}
\usepackage{booktabs}
\usepackage{longtable}

\newcommand{\appropto}{\mathrel{\vcenter{
      \offinterlineskip\halign{\hfil$##$\cr
        \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}

@@

\title{When does vapor pressure deficit drive or reduce
  evapotranspiration?}
\Author[1]{Adam}{Massmann}
\Author[1]{Pierre}{Gentine}
\Author[1,2]{Changjie}{Lin}

@@

\runningtitle{When does VPD drive or reduce ET?}

\runningauthor{A. Massmann}

\correspondence{Adam Massmann (akm2203@columbia.edu)}

\firstpage{1}

\maketitle

\begin{abstract}
\input{abstract.tex}
\end{abstract}

\introduction
\input{intro.tex}

@@

\conclusions
\input{conclusions.tex}

\codedataavailability{All code and data used
in this analysis, including those used to generate the figures and
tables, are publicly available at
\url{https://github.com/massma/climate\_et}}

\appendix

\section{FLUXNET2015 sites}\label{flux_sites}

\appendixtables   %% needs to be added in front of appendix tables

% below taken adapted from Trevor Keenan's FLUXNET citations
% at github.com/trevorkeenan/FLUXNET_citations
Table A1: Metadata and citations for flux sites used in this analysis. All data are gathered from \url{www.fluxdata.org}, and citations are aggregated using tools available at \url{https://github.com/trevorkeenan/FLUXNET_citations}.
\begin{longtable}{l l l l l l l}
  \hline
  \textbf{Site} &
  \textbf{PFT} &
  \textbf{Lat} &
  \textbf{Lon} &
  \textbf{Clim\textsuperscript{1}} &
  \textbf{Period} &
  \textbf{References} \\
  [0.5ex]
  \hline
  \input{flux_sites.tex}
  [1ex]
  \hline
\end{longtable}
\textsuperscript{1}  K{\"o}ppen Climate classification.

\authorcontribution{AM: formal analysis; methodology; software;
  validation; visualization; writing - original draft. PG:
  conceptualization; methodology; supervision; writing - review \&
  editing. CL: data curation; writing - review \& editing.}

\competinginterests{We declare no competing interests.}

\begin{acknowledgements}
This work used eddy covariance data acquired and shared
by the FLUXNET community, including these networks: AmeriFlux, AfriFlux,
AsiaFlux, CarboAfrica, CarboEuropeIP, CarboItaly, CarboMont,
ChinaFlux, Fluxnet-Canada, GreenGrass, ICOS, KoFlux, LBA, NECC,
OzFlux-TERN, TCOS-Siberia, and USCCC. The ERA-Interim reanalysis data
are provided by ECMWF and processed by LSCE. The FLUXNET eddy covariance
data processing and harmonization was carried out by the European Fluxes
Database Cluster, AmeriFlux Management Project, and Fluxdata project of
FLUXNET, with the support of CDIAC and ICOS Ecosystem Thematic Center,
and the OzFlux, ChinaFlux and AsiaFlux offices. We would like to thank
Dr. Trevor Keenan for providing tools for citation of the FLUXNET2015
dataset, available at
\url{https://github.com/trevorkeenan/FLUXNET_citations}. This material is
based upon work supported by the National Science Foundation Graduate
Research Fellowship under Grant No. DGE 16-44869.
%\hyperref[https://github.com/massma/climate\_et]{https://github.com/massma/climate_et}.
\end{acknowledgements}

\bibliographystyle{copernicus}
\bibliography{references.bib}
